---
title: "TABA_Assignment 2"
author: "Surendra Kumar Dattatrey"
date: "13 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE)
```

## R Markdown
This markdown document is for assignment 2 of TABA. Where i performed analysis on wiki page of Bank of America. Reason of choosing this fortune 500 company, is that i have already worked this organization and i like this orgazation due it's work culture. During my tenure with this organization, i worked a lot and enjoyed a lot.

```{r cars}
rm(list=ls())
library(rvest)
library(NLP)
library(openNLP)
library(rworldmap)
library(stringr)
library(ggplot2)
library(ggmap)

page = read_html('https://en.wikipedia.org/wiki/Bank_of_America')

text = html_text(html_nodes(page,'p'))
text = text[text != ""]
text = gsub("\\[[0-9]]|\\[[0-9][0-9]]|\\[[0-9][0-9][0-9]]","",text) # removing refrences [101] type



# Make one complete document
text = paste(text,collapse = " ") 
text = as.String(text)
sent_annot = Maxent_Sent_Token_Annotator()
word_annot = Maxent_Word_Token_Annotator()
loc_annot = Maxent_Entity_Annotator(kind = "location")

annot.l1 = NLP::annotate(text, list(sent_annot,word_annot,loc_annot))

k <- sapply(annot.l1$features, `[[`, "kind")
boa_locations = text[annot.l1[k == "location"]]

all_places = unique(boa_locations) # view contents of this obj

all_places_geocoded <- geocode(all_places) 
#all_places_geocoded 

```

## Number and Currency Data extraction 
I try to exracted and segregated data in two ways,
1) Currency data 
2) Number data. 
During my extraction, i found that currency data is in USD.

```{r}
extract_dollar_amount <- str_extract_all(text,"\\$[0-9].[0-9]*\\b ")
extract_dollar_amount

extract_all_numbers <- str_extract_all(text,"\\(?[0-9].[0-9]+\\)? | \\(?[0-9][0-9],[0-9]+\\)?")[[1]]
extract_all_numbers


```

## Plotting location of BOA

Locations are plotted for BOA which I extracted in previous step.

```{r pressure, echo=FALSE}
newmap <- getMap(resolution = "low")
plot(newmap)

points(all_places_geocoded$lon, all_places_geocoded$lat, col = "blue", cex = 1.2, pch = 19)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
