---
title: "TABA_Assignment 2"
author: "Surendra Kumar Dattatrey"
date: "13 May 2017"
output: html_document
---

## R Markdown

This markdown document is for assignment 2 of TABA. Where i performed analysis on Bank of America, with some good reason as previously i have worked in this organization and i like the work culture of this organization.

```{r cars}
rm(list=ls())
library(rvest)
library(NLP)
library(openNLP)
library(rworldmap)
library(stringr)
library(ggplot2)
library(ggmap)

page = read_html('https://en.wikipedia.org/wiki/Bank_of_America')

text = html_text(html_nodes(page,'p'))
text = text[text != ""]
text = gsub("\\[[0-9]]|\\[[0-9][0-9]]|\\[[0-9][0-9][0-9]]","",text) # removing refrences [101] type

```
## Number and Currency Data extraction 

```{r}
extract_dollar_amount <- str_extract_all(text,"\\$[0-9].[0-9]*\\b ")
extract_dollar_amount

extract_all_numbers <- str_extract_all(text,"\\(?[0-9].[0-9]+\\)? | \\(?[0-9][0-9],[0-9]+\\)?")[[1]]
extract_all_numbers

# Make one complete document
text = paste(text,collapse = " ") 
text = as.String(text)
sent_annot = Maxent_Sent_Token_Annotator()
word_annot = Maxent_Word_Token_Annotator()
loc_annot = Maxent_Entity_Annotator(kind = "location")

annot.l1 = NLP::annotate(text, list(sent_annot,word_annot,loc_annot))

k <- sapply(annot.l1$features, `[[`, "kind")
boa_locations = text[annot.l1[k == "location"]]

all_places = unique(boa_locations) # view contents of this obj

all_places_geocoded <- geocode(all_places) 
#all_places_geocoded 

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

newmap <- getMap(resolution = "low")
plot(newmap)
#plot(newmap, asp = 1)

points(all_places_geocoded$lon, all_places_geocoded$lat, col = "blue", cex = 1.2, pch = 19)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
